---
title: "PATNET Seminar Project Group C"
subtitle:  "A Network Analysis on German Wind Motor Industry"
author: "Jhalak Gope"
date: '2022-07-13'
output:
  html_document:
    code_download: true
    css: css_back.css
    theme: yeti
    toc_depth: 5
    toc: true
    toc_float: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(warning = FALSE)
```

# General Data Preparation

## Loading Libraries

```{r loading libraries, warning=FALSE, results="hide"}
suppressMessages(library(sna))
suppressMessages(library(dplyr))
suppressMessages(library(ggsci))
suppressMessages(library(plotly))
suppressMessages(library(igraph))
suppressMessages(library(network))
suppressMessages(library(igraphdata))
suppressMessages(library(intergraph))
suppressMessages(library(RColorBrewer))
```

## Loading Dataset

```{r loading dataset}
load("res_sem.RData")
#sub stringing the IPC3 from IPC
IPC4 <- substr(joined_IPC_Inv$IPC, start = 1, stop = 4) #extracting the IPC3 from the original sorted dataset
IPC4 <- as.data.frame(IPC4) # defining it as a dataframe
data_final <- cbind(joined_IPC_Inv, IPC4) # combining the newly created IPC3 containing dataframe with the main dataframe
rm(joined_IPC_Inv) & rm(IPC4) # removing the dataset to free memory
data_final <- subset(data_final, select = -c(IPC,ctry_code)) # dropping columns
```

## Data Cleaning

```{r data cleaning}
data <- (data_final %>% 
                 filter(IPC4=="F03D")) # creating subset of Wind Energy Industry (F03D)
rm(data_final)
data <- (data %>% 
           filter(app_year>= 1996 & app_year <= 2016)) # limiting years from 1996 to 2016

# now getting rid of empty city values
data <- (data %>%
           mutate(city = replace(city, city == "", NA)))#making the empty values NA
data <- na.omit(data) #getting rid of NA values

# getting rid of duplicate values
data_main <- data[!duplicated(data),]

# ranking cities according to patents
data_main_city_rank <- (data_main %>% 
                          group_by(city) %>%
                          count(city, sort = TRUE,  name = "patents")) #ranking the cities according to the number of patent applications

data_main_15 <- head(data_main_city_rank,15) # keeping first 15 patent owning cities in ranked format
data_main_15_attr <- (data_main %>%
                     filter(city %in% c("Aurich","Hamburg","Berlin","Salzbergen","Rendsburg","Rheine","Kiel","Aachen","Munchen","Norderstedt","Osnabruck","Bremen","Erlangen","Dresden","Munster"))) # keeping the most 15 patent owning cities with all attributes
```

# General Insights from the Data

## Top 15 most patent owning cities

```{r top most innovative cities, echo=FALSE, fig.height=7, fig.width=8, results="asis"}
plot_ly(data_main_15,
        x = data_main_15$city,
        y = data_main_15$patents,
        type = "bar",
        color = data_main_15$city,
        showlegend = FALSE,
        colors=pal_jco()(10)) %>% 
  layout(title = "Top 15 German Cities in Wind Motor Innovation",
         xaxis = list(title = "",
                      categoryorder = "array",
                      categoryarray = ~city),
         yaxis = list(title = "Number of patents")
         )
```

# Network Data Preparation (Using igraph and sna packages)

## N1. Inventor networks for all cities

```{r inv net all cities}
inv_aff_all <- (data_main %>% 
              select(appln_id,person_id))
inv_aff_all_2mode <- table(inv_aff_all)
inv_aff_all_adj <- inv_aff_all_2mode %*% t(inv_aff_all_2mode)
diag(inv_aff_all_adj) <-0 # deleting the diagonals
inv_aff_all_ig <- graph.adjacency(inv_aff_all_adj, mode = "undirected", weight = TRUE)
print(inv_aff_all_ig) # Basic information about the network
```

## N2. City networks (for 15 most innovative cities)

```{r city net 15 cities}
inv_city <- (data_main_15_attr %>% 
               select(city,appln_id))
inv_city_2mode <-  table(inv_city)   # cross tabulate -> 2-mode sociomatrix
inv_city_adj <- inv_city_2mode %*% t(inv_city_2mode)
diag(inv_city_adj) <-0 # deleting the diagonals
inv_city_ig <- graph.adjacency(inv_city_adj, mode = "undirected", weight = TRUE)
print(inv_city_ig) # basic information about the network

```

## N3. Inventor's network of top 15 cities

```{r inv net}
# inventor's data cleaning
inv_person <- (data_main_15_attr %>% 
                 select(inv_name,appln_id)) # sub-setting the data for inventors with patents
inv_per_attr <- (data_main_15_attr %>% 
                   select(appln_id, city))

# parsing the person's network data to have clean and non-duplicated values
inv_person_parsed <- inv_person
length(unique(inv_person_parsed$inv_name))
inv_person_parsed$inv_name_small <- tolower(inv_person_parsed$inv_name)
inv_person_parsed$inv_name_small <- sub(", prof. dr.-ing.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(", dr.-ing.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(", dipl.-ing.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(", -ing.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(", dr.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(" dr.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))

# new network changed size
length(unique(inv_person_parsed$inv_name_small))/length(unique(inv_person_parsed$inv_name))

# getting rid of original inventor names
inv_person_parsed$inv_name <- inv_person_parsed$inv_name_small

# removing third column
inv_person_parsed <- subset(inv_person_parsed, select = -c(inv_name_small))

# creating network with the cleaned data
inv_person_2mode <- table(inv_person_parsed) # making 2 mode sociomatrix
inv_person_adj <- inv_person_2mode %*% t(inv_person_2mode)
diag(inv_person_adj) <-0
inv_aff_ig <- graph.adjacency(inv_person_adj, mode = "undirected", weight = TRUE)


```

# Creating Networks and Plotting Graphs

Detaching packages to avoid conflicts between package operations.

```{r library detaching, message=FALSE, warning=FALSE}
detach(package:sna)
detach(package:network)
suppressMessages(library(igraph))
```

## N1. Creating the network for all the inventors

```{r conv. n1}
# matching the dataset with city and application ids
inv_person_parsed$city <- inv_per_attr$city[match(inv_person_parsed$appln_id, inv_person_parsed$appln_id)]
```

### N1. Plotting

```{r n1 plot, fig.height=7, fig.width=7}
set.seed(100)
par(mar=c(0,0,1,0))
plot(inv_aff_all_ig,
     vertex.label=NA,
     vertex.size = 3,
     vertex.color = V(inv_aff_all_ig),
     main="Network of all the inventors")
```

## N2. Creating network for 15 cities

```{r conv. n2}
inv_city_ig <- (inv_city_ig %>% 
                  set_vertex_attr(
                    name = "vertex.names",
                    value = c("Aurich","Hamburg","Berlin","Salzbergen","Rendsburg","Rheine","Kiel","Aachen","Munchen","Norderstedt","Osnabruck","Bremen","Erlangen","Dresden","Munster") # modifying vertex names on the igraph object (as city names)
                  ))
V(inv_city_ig)$label <- c("Aurich","Hamburg","Berlin","Salzbergen","Rendsburg","Rheine","Kiel","Aachen","Munchen","Norderstedt","Osnabruck","Bremen","Erlangen","Dresden","Munster") # changing the igraph object's labels also into the city names
```

### N2. Centrality Measurement

```{r n2 centrality}
centr_degree(
  inv_city_ig,
  mode = c("all", "out", "in", "total"),
  loops = F,
  normalized = TRUE)
```

### N2. Plotting

```{r n2 plot, fig.height=6, fig.width=6}
par(mar=c(0,0,2,0))
set.seed(100)
plot(inv_city_ig,
     vertex.label=V(inv_city_ig)$city,
     vertex.color=V(inv_city_ig),
     vertex.size= degree(inv_city_ig)*3,
     vertex.frame.color=NA,
     vertex.label.family= "Cambria",
     vertex.label.font=2,
     main="Network of top 15 cities \n (according to their density)")
```

## N3. Plotting and centrality measurement of inventor's network (top 15 cities) 
### N3. Centrality Measurement

```{r n3 centrality}
centr_degree(
  inv_aff_ig,
  mode = c("all", "out", "in", "total"),
  loops = F,
  normalized = TRUE)
```

### N3. Plotting

#### General network graph

```{r general net plot, fig.height=6, fig.width=6}
set.seed(100)
par(mar=c(0,0,2,0))
plot(inv_aff_ig,
     vertex.label=NA,
     vertex.size=1.5,
     vertex.frame.color="black",
     vertex.color = V(inv_aff_ig),
     main="Inventor network of top 15 cities\nfor 1996-2016")
```

#### Plotting with density

```{r  density plot, fig.height=6, fig.width=6}
set.seed(100)
par(mar=c(0,0,1,0))
plot(inv_aff_ig,
     vertex.label=NA,
     vertex.size=degree(inv_aff_ig)*1.5,
     vertex.frame.color="black",
     vertex.color = V(inv_aff_ig),
     main="Inventor network of top 15 cities\nfor 1996-2016\nwith degree measurement")
```

#### Plotting with density and edge betweenness

```{r  density, eb plot, fig.height=6, fig.width=6}
set.seed(100)
par(mar=c(0,0,4,0))
plot(inv_aff_ig,
     vertex.label=NA,
     vertex.frame.color="black",
     vertex.color=V(inv_aff_ig),
     vertex.size=degree(inv_aff_ig)*1.5,
     edge.curved=.1,
     main="Inventor network of top 15 cities\nfor 1996-2016\nwith degree measurement and edge betweenness",
     edge.width = edge_betweenness(inv_aff_ig)*.8)
```

# Top 5 City's Innovation Scenario over the Time

Detaching packages to avoid conflicts between package operations

```{r pckg detach}
detach(package:igraph)
suppressMessages(library(network))
```

## Aurich

```{r aurich net}
## Aurich 1996:2006 network
aurich_data_06 <- (data_main_15_attr %>%
                          filter(city=="Aurich", app_year>=1996 & app_year<=2006) %>%
                          select(inv_name, appln_id))

aurich_data_06 <- table(aurich_data_06)
dim(aurich_data_06)
aurich_adj_06 <- aurich_data_06 %*% t(aurich_data_06)
dim(aurich_adj_06)
class(aurich_adj_06)
aurich_nw_06 <-  network(aurich_adj_06,
                      matrix.type="adjacency",
                      directed=F)  # convert into 'network' format


## Aurich 2007:2016 network
aurich_data_16 <- (data_main_15_attr %>%
                        filter(city=="Aurich", app_year>=2007 & app_year<=2016) %>%
                        select(inv_name, appln_id))

aurich_data_16 <- table(aurich_data_16)
dim(aurich_data_16)
aurich_adj_16 <- aurich_data_16 %*% t(aurich_data_16)
dim(aurich_adj_16)
class(aurich_adj_16)
aurich_nw_16 <-  network(aurich_adj_16,
                           matrix.type="adjacency",
                           directed=F)  # convert into 'network' format

```

### Plotting

```{r aurich plot, fig.height=6, fig.width=8}
par(mfrow = c(1,2))
par(mar=c(3,0,1,0))

#plot for 1996:2006
plot.network(aurich_nw_06,
             vertex.col="#7570B3",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for Aurich 1996:2006",
             pad=4,
             frame = T,
             sub=network.size(aurich_nw_06),
             cex.main=.8)

# plot for 2007:2016
plot.network(aurich_nw_16,
             vertex.col="#7570B3",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for Aurich 2007:2016",
             frame = T,
             cex.main=.8)
cat("Total nodes 1996-2006:", network.size(aurich_nw_06),"\nTotal nodes 2007-2016:", network.size(aurich_nw_16))
```

## Hamburg

```{r hamburg net}
## Hamburg 1996:2006 network
hamburg_data_06 <- (data_main_15_attr %>%
                          filter(city=="Hamburg", app_year>=1996 & app_year<=2006) %>%
                          select(inv_name, appln_id))

hamburg_data_06 <- table(hamburg_data_06)
dim(hamburg_data_06)
hamburg_adj_06 <- hamburg_data_06 %*% t(hamburg_data_06)
dim(hamburg_adj_06)
class(hamburg_adj_06)
hamburg_nw_06 <-  network(hamburg_adj_06,
                         matrix.type="adjacency",
                         directed=F)  # convert into 'network' format


## Hamburg 2007:2006 network
hamburg_data_16 <- (data_main_15_attr %>%
                          filter(city=="Hamburg", app_year>=2007 & app_year<=2016) %>%
                          select(inv_name, appln_id))

hamburg_data_16 <- table(hamburg_data_16)
dim(hamburg_data_16)
hamburg_adj_16 <- hamburg_data_16 %*% t(hamburg_data_16)
dim(hamburg_adj_16)
class(hamburg_adj_16)
hamburg_nw_16 <-  network(hamburg_adj_16,
                      matrix.type="adjacency",
                      directed=F)  # convert into 'network' format

```

### Plotting

```{r hamburg plot, fig.height=6, fig.width=8}
par(mfrow = c(1,2))
par(mar=c(0,0,1,0))

#plot for 1996:2006
plot.network(hamburg_nw_06,
             vertex.col="#99B898",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for Hamburg 1996:2006",
             frame = T,
             pad=4,
             cex.main=.8)
# plot for 2007:2016
plot.network(hamburg_nw_16,
             vertex.col="#99B898",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for Hamburg 2007:2016",
             frame = T,
             cex.main=.8)
cat("Total nodes 1996-2006:", network.size(hamburg_nw_06),"\nTotal nodes 2007-2016:", network.size(hamburg_nw_16))
```

## Berlin

```{r berlin net}
## Berlin 1996:2006 network
berlin_data_06 <- (data_main_15_attr %>%
                      filter(city=="Berlin", app_year>=1996 & app_year<=2006) %>%
                      select(inv_name, appln_id))

berlin_data_06 <- table(berlin_data_06)
dim(berlin_data_06)
berlin_adj_06 <- berlin_data_06 %*% t(berlin_data_06)
dim(berlin_adj_06)
class(berlin_adj_06)
berlin_nw_06 <-  network(berlin_adj_06,
                          matrix.type="adjacency",
                          directed=F)  # convert into 'network' format


## Berlin 2007:2016 network
berlin_data_16 <- (data_main_15_attr %>%
                      filter(city=="Berlin", app_year>=2007 & app_year<=2016) %>%
                      select(inv_name, appln_id))

berlin_data_16 <- table(berlin_data_16)
dim(berlin_data_16)
berlin_adj_16 <- berlin_data_16 %*% t(berlin_data_16)
dim(berlin_adj_16)
class(berlin_adj_16)
berlin_nw_16 <-  network(berlin_adj_16,
                          matrix.type="adjacency",
                          directed=F)  # convert into 'network' format

```

### Plotting

```{r berlin plot, fig.height=6, fig.width=8}
par(mfrow = c(1,2))
par(mar=c(0,0,1,0))

#plot for 1996:2006
plot.network(berlin_nw_06,
             vertex.col="#F26B38",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for Berlin 1996:2006",
             frame = T,
             pad=4,
             cex.main=.8)
# plot for 2007:2016
plot.network(berlin_nw_16,
             vertex.col="#F26B38",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for Berlin 2007:2016",
             frame = T,
             cex.main=.8)
cat("Total nodes 1996-2006:", network.size(berlin_nw_06),"\nTotal nodes 2007-2016:", network.size(berlin_nw_16))

```

## Salzbergen

```{r salzbergen net}
## Salzbergen 1996:2006 network
salzbergen_data_06 <- (data_main_15_attr %>%
                         filter(city=="Salzbergen", app_year>=1996 & app_year<=2006) %>%
                         select(inv_name, appln_id))

salzbergen_data_06 <- table(salzbergen_data_06)
dim(salzbergen_data_06)
salzbergen_adj_06 <- salzbergen_data_06 %*% t(salzbergen_data_06)
dim(salzbergen_adj_06)
class(salzbergen_adj_06)
salzbergen_nw_06 <-  network(salzbergen_adj_06,
                         matrix.type="adjacency",
                         directed=F)  # convert into 'network' format


## Salzbergen 2007:2017 network
salzbergen_data_16 <- (data_main_15_attr %>%
                         filter(city=="Salzbergen", app_year>=2007 & app_year<=2016) %>%
                         select(inv_name, appln_id))

salzbergen_data_16 <- table(salzbergen_data_16)
dim(salzbergen_data_16)
salzbergen_adj_16 <- salzbergen_data_16 %*% t(salzbergen_data_16)
dim(salzbergen_adj_16)
class(salzbergen_adj_16)
salzbergen_nw_16 <-  network(salzbergen_adj_16,
                             matrix.type="adjacency",
                             directed=F)  # convert into 'network' format

```

### Plotting

```{r salzbergen plot, fig.height=6, fig.width=8}
par(mfrow = c(1,2))
par(mar=c(0,0,1,0))

#plot for 1996:2006
plot.network(salzbergen_nw_06,
             vertex.col="#594F4F",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for salzbergen 1996:2006",
             frame = T,
             pad=4,
             cex.main=.8)
# plot for 2007:2016
plot.network(salzbergen_nw_16,
             vertex.col="#594F4F",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for salzbergen 2007:2016",
             frame = T,
             cex.main=.8)
cat("Total nodes 1996-2006:", network.size(salzbergen_nw_06),"\nTotal nodes 2007-2016:", network.size(salzbergen_nw_16))

```

## Rendsburg

```{r rendsburg net}
## Rendsburg 1996:2006 network
rendsburg_data_06 <- (data_main_15_attr %>%
                         filter(city=="Rendsburg", app_year>=1996 & app_year<=2006) %>%
                         select(inv_name, appln_id))

rendsburg_data_06 <- table(rendsburg_data_06)
dim(rendsburg_data_06)
rendsburg_adj_06 <- rendsburg_data_06 %*% t(rendsburg_data_06)
dim(rendsburg_adj_06)
class(rendsburg_adj_06)
rendsburg_nw_06 <-  network(rendsburg_adj_06,
                             matrix.type="adjacency",
                             directed=F)  # convert into 'network' format


## Rendsburg 200:2016 network
rendsburg_data_16 <- (data_main_15_attr %>%
                         filter(city=="Rendsburg", app_year>=2007 & app_year<=2016) %>%
                         select(inv_name, appln_id))

rendsburg_data_16 <- table(rendsburg_data_16)
dim(rendsburg_data_16)
rendsburg_adj_16 <- rendsburg_data_16 %*% t(rendsburg_data_16)
dim(rendsburg_adj_16)
class(rendsburg_adj_16)
rendsburg_nw_16 <-  network(rendsburg_adj_16,
                             matrix.type="adjacency",
                             directed=F)  # convert into 'network' format


```

### Plotting

```{r rendsburg plot, fig.height=6, fig.width=8}
par(mfrow = c(1,2))
par(mar=c(0,0,1,0))

#plot for 1996:2006
plot.network(rendsburg_nw_06,
             vertex.col="#355C7D",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for Rendsburg 1996:2006",
             frame = T,
             pad=4,
             cex.main=.8)
# plot for 2007:2016
plot.network(rendsburg_nw_16,
             vertex.col="#355C7D",
             vertex.cex=1,
             vertex.border="black",
             main="Inventors Network for Rendsburg 2007:2016",
             frame = T,
             cex.main=.8)
cat("Total nodes 1996-2006:", network.size(rendsburg_nw_06),"\nTotal nodes 2007-2016:", network.size(rendsburg_nw_16))
```

# Position of the Top 5 Cities in 15 City's Network

Detaching packages to avoid conflicts between package operations.

```{r detaching libraries}
detach(package:network)
suppressMessages(library(igraph))
```

## Aurich

```{r aurich position}
## position of the cities in the overall network
inv_person_parsed$city <- inv_per_attr$city[match(inv_person_parsed$appln_id, inv_person_parsed$appln_id)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)
V(inv_aff_ig)$city_name <- inv_person_parsed$city[match(V(inv_aff_ig)$id, inv_person_parsed$inv_name)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)

V(inv_aff_ig)$city_name_color <- ifelse(V(inv_aff_ig)$city_name == "Aurich", "red","azure1")
#V(inv_aff_ig)$id[degree(inv_aff_ig)>5]
#degree(inv_aff_ig)

set.seed(100)
par(mar=c(0,0,1,0))
plot(inv_aff_ig,
     layout = layout.auto(inv_aff_ig),
     vertex.size = 3,
     vertex.frame.color="black",
     vertex.color = V(inv_aff_ig)$city_name_color,
     vertex.label = NA,
     edge.color= "black",
     main="Inventor's from Aurich in top 15 city's network")

```

## Hamburg

```{r hamburg position}
## position of the cities in the overall network
inv_person_parsed$city <- inv_per_attr$city[match(inv_person_parsed$appln_id, inv_person_parsed$appln_id)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)
V(inv_aff_ig)$city_name <- inv_person_parsed$city[match(V(inv_aff_ig)$id, inv_person_parsed$inv_name)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)

V(inv_aff_ig)$city_name_color <- ifelse(V(inv_aff_ig)$city_name == "Hamburg", "blue","azure1")
#V(inv_aff_ig)$id[degree(inv_aff_ig)>5]
#degree(inv_aff_ig)

set.seed(100)
par(mar=c(0,0,1,0))
plot(inv_aff_ig,
     layout = layout.auto(inv_aff_ig),
     vertex.size = 3,
     vertex.frame.color="black",
     vertex.color = V(inv_aff_ig)$city_name_color,
     vertex.label = NA,
     edge.color= "black",
     main="Inventor's from Hamburg in top 15 city's network")

```

## Berlin

```{r berlin position}
## position of the cities in the overall network
inv_person_parsed$city <- inv_per_attr$city[match(inv_person_parsed$appln_id, inv_person_parsed$appln_id)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)
V(inv_aff_ig)$city_name <- inv_person_parsed$city[match(V(inv_aff_ig)$id, inv_person_parsed$inv_name)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)

V(inv_aff_ig)$city_name_color <- ifelse(V(inv_aff_ig)$city_name == "Berlin", "darkslategray4","azure1")
#V(inv_aff_ig)$id[degree(inv_aff_ig)>5]
#degree(inv_aff_ig)

set.seed(100)
par(mar=c(0,0,1,0))
plot(inv_aff_ig,
     layout = layout.auto(inv_aff_ig),
     vertex.size = 3,
     vertex.frame.color="black",
     vertex.color = V(inv_aff_ig)$city_name_color,
     vertex.label = NA,
     edge.color= "black",
     main="Inventor's from Berlin in top 15 city's network")
```

## Salzbergen

```{r salzbergen position}
## position of the cities in the overall network
inv_person_parsed$city <- inv_per_attr$city[match(inv_person_parsed$appln_id, inv_person_parsed$appln_id)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)
V(inv_aff_ig)$city_name <- inv_person_parsed$city[match(V(inv_aff_ig)$id, inv_person_parsed$inv_name)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)

V(inv_aff_ig)$city_name_color <- ifelse(V(inv_aff_ig)$city_name == "Salzbergen", "darkorange1","azure1")
#V(inv_aff_ig)$id[degree(inv_aff_ig)>5]
#degree(inv_aff_ig)

set.seed(100)
par(mar=c(0,0,1,0))
plot(inv_aff_ig,
     layout = layout.auto(inv_aff_ig),
     vertex.size = 3,
     vertex.frame.color="black",
     vertex.color = V(inv_aff_ig)$city_name_color,
     vertex.label = NA,
     edge.color= "black",
     main="Inventor's from Salzbergen in top 15 city's network")
```

## Rendsburg

```{r rendsburg position}
## position of the cities in the overall network
inv_person_parsed$city <- inv_per_attr$city[match(inv_person_parsed$appln_id, inv_person_parsed$appln_id)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)
V(inv_aff_ig)$city_name <- inv_person_parsed$city[match(V(inv_aff_ig)$id, inv_person_parsed$inv_name)]
V(inv_aff_ig)$id <- colnames(inv_person_adj)

V(inv_aff_ig)$city_name_color <- ifelse(V(inv_aff_ig)$city_name == "Rendsburg", "darkmagenta","azure1")
#V(inv_aff_ig)$id[degree(inv_aff_ig)>5]
#degree(inv_aff_ig)

set.seed(100)
par(mar=c(0,0,1,0))
plot(inv_aff_ig,
     layout = layout.auto(inv_aff_ig),
     vertex.size = 3,
     vertex.frame.color="black",
     vertex.color = V(inv_aff_ig)$city_name_color,
     vertex.label = NA,
     edge.color= "black",
     main="Inventor's from Rendsburg in top 15 city's network")
```
