---
title: "PATNET Seminar Project"
author: "Jhalak Gope"
date: '2022-06-21'
output:
  html_document:
    theme: yeti
    toc_depth: 5
    toc: true
    toc_float: true
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

# General Data Preparation

## Loading Libraries

```{r, warning=FALSE, results="hide"}
library(dplyr)
library(sna)
library(network)
library(networkD3)
library(intergraph)
```

## Loading Dataset

```{r}
load("res_sem.RData")
#sub stringing the IPC3 from IPC
IPC4 <- substr(joined_IPC_Inv$IPC, start = 1, stop = 4) #extracting the IPC3 from the original sorted dataset
IPC4 <- as.data.frame(IPC4) # defining it as a dataframe
data_final <- cbind(joined_IPC_Inv, IPC4) # combining the newly created IPC3 containing dataframe with the main dataframe
rm(joined_IPC_Inv) & rm(IPC4) # removing the dataset to free memory
data_final <- subset(data_final, select = -c(IPC,ctry_code)) # dropping columns
```

## Data cleaning

```{r}
data <- (data_final %>% 
                 filter(IPC4=="F03D")) # creating subset of Wind Energy Industry (F03D)
rm(data_final)
data <- (data %>% 
           filter(app_year>= 1996 & app_year <= 2016)) # limiting years from 1996 to 2016

# now getting rid of empty city values
data <- (data %>%
           mutate(city = replace(city, city == "", NA)))#making the empty values NA
data <- na.omit(data) #getting rid of NA values

# getting rid of duplicate values
data_main <- data[!duplicated(data),]

# ranking cities according to patents
data_main_city_rank <- (data_main %>% 
                          group_by(city) %>%
                          count(city, sort = TRUE,  name = "patents")) #ranking the cities according to the number of patent applications

data_main_15 <- head(data_main_city_rank,15) # keeping first 15 patent owning cities in ranked format
data_main_15_attr <- (data_main %>%
                     filter(city %in% c("Aurich","Hamburg","Berlin","Salzbergen","Rendsburg","Rheine","Kiel","Aachen","Munchen","Norderstedt","Osnabruck","Bremen","Erlangen","Dresden","Munster"))) # keeping the most 15 patent owning cities with all attributes
```

# General Insights from the Data

## Top 15 most patent owning cities

```{r, results="asis"}
data_main_15 %>%
  knitr::kable(caption = "Top 15 German Cities in Wind Motor Innovation") %>% 
  kableExtra::kable_styling(bootstrap_options = c("hover", "bordered"), full_width = FALSE)
```

# Network Data Preparation (Using network and sna pckages)

## N1. Inventors networks for all cities

```{r}
inv_aff_all <- (data_main %>% 
              select(appln_id,person_id))
inv_aff_all_2mode <- table(inv_aff_all)
inv_aff_all_adj <- inv_aff_all_2mode %*% t(inv_aff_all_2mode)
inv_aff_all_nw <-  network(inv_aff_all_adj,
                       matrix.type="adjacency",
                       directed=F)  # convert into 'network' format
print.network(inv_aff_all_nw) # Basic information about the network
```

## N2. City networks (for 15 most innovative cities)

```{r}
inv_city <- (data_main_15_attr %>% 
               select(city,appln_id))
inv_city_2mode <-  table(inv_city)   # cross tabulate -> 2-mode sociomatrix
inv_city_adj <- inv_city_2mode %*% t(inv_city_2mode)
inv_city_nw <-  network(inv_city_adj,
                        matrix.type="adjacency",
                        directed=F)  # convert into 'network' format
print.network(inv_city_nw) # basic information about the network
```

## N3. Inventor's (person's) network

```{r}
# inventor's data cleaning
inv_person <- (data_main_15_attr %>% 
                 select(inv_name,appln_id)) # sub-setting the data for inventors with patents
inv_per_attr <- (data_main_15_attr %>% 
                   select(appln_id, city))

# parsing the person's network data to have clean and non-duplicated values
inv_person_parsed <- inv_person
length(unique(inv_person_parsed$inv_name))
inv_person_parsed$inv_name_small <- tolower(inv_person_parsed$inv_name)
inv_person_parsed$inv_name_small <- sub(", prof. dr.-ing.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(", dr.-ing.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(", dipl.-ing.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(", -ing.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(", dr.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))
inv_person_parsed$inv_name_small <- sub(" dr.","", inv_person_parsed$inv_name_small)
length(unique(inv_person_parsed$inv_name_small))

# new network changed size
length(unique(inv_person_parsed$inv_name_small))/length(unique(inv_person_parsed$inv_name))

# getting rid of original inventor names
inv_person_parsed$inv_name <- inv_person_parsed$inv_name_small

# removing third column
inv_person_parsed <- subset(inv_person_parsed, select = -c(inv_name_small))

# creating network with the cleaned data
inv_person_2mode <- table(inv_person_parsed) # making 2 mode sociomatrix
inv_person_adj <- inv_person_2mode %*% t(inv_person_2mode)
inv_person_nw <- network(inv_person_adj,
                         directed = F)

```

# Conversion and plotting graphs

Detaching packages to avoid conflicts between package operations.

```{r}
detach(package:sna)
detach(package:network)
library(igraph)
```

## N1. Converting the network for all the inventors

```{r}
inv_aff_ig <- asIgraph(inv_aff_all_nw)
class(inv_aff_all)
```

### N1. Plotting

```{r}
set.seed(100)
par(mar=c(0,0,1,0))
plot(inv_aff_ig,
     layout = layout.auto(inv_aff_ig),
     vertex.size = 2,
     vertex.label = NA,
     main="Network of all the inventors")
```

## N2. Converting the network package object into igraph object (for 15 cities)

```{r}
inv_city_ig <- asIgraph(inv_city_nw)
class(inv_city_ig)

inv_city_ig <- (inv_city_ig %>% 
                  set_vertex_attr(
                    name = "vertex.names",
                    value = c("Aurich","Hamburg","Berlin","Salzbergen","Rendsburg","Rheine","Kiel","Aachen","Munchen","Norderstedt","Osnabruck","Bremen","Erlangen","Dresden","Munster") # modifying vertex names on the igraph object (as city names)
                  ))
V(inv_city_ig)$label <- c("Aurich","Hamburg","Berlin","Salzbergen","Rendsburg","Rheine","Kiel","Aachen","Munchen","Norderstedt","Osnabruck","Bremen","Erlangen","Dresden","Munster") # changing the igraph object's labels also into the city names
```

### N2. Centrality Measurement

```{r}
centr_degree(
  inv_city_ig,
  mode = c("all", "out", "in", "total"),
  loops = F,
  normalized = TRUE)
```

### N2. Plotting

```{r}
par(mar=c(0,0,2,0))
set.seed(100)
plot(inv_city_ig,
     vertex.label=V(inv_city_ig)$city,
     vertex.color=V(inv_city_ig),
     vertex.size= degree(inv_city_ig)*3,
     vertex.frame.color=NA,
     vertex.label.family= "Cambria",
     vertex.label.font=2,
     main="Network of top 15 cities \n (according to their density)")
```

## N3. Converting the network package object into igraph object (for 15 cities)

```{r}
inv_person_ig <- asIgraph(inv_person_nw)
set_vertex_attr(graph = inv_person_ig, name = "city", value = "city")
```

### N3. Centrality Measurement

```{r}
centr_degree(
  inv_person_ig,
  mode = c("all", "out", "in", "total"),
  loops = F,
  normalized = TRUE)
```

### N3. Plotting

#### General network graph

```{r}
par(mar=c(0,0,1,0))
set.seed(100)
plot(inv_person_ig,
     vertex.label=NA,
     vertex.frame.color=NA,
     vertex.color=V(inv_person_ig),
     vertex.size=2,
     edge.colour="black",
     main="Inventor's network for top 15 cities",
     sub=("(on edge betweenness of the inventors)"))
```

#### plotting with edge betweenness

```{r}
par(mar=c(0,0,1,0))
plot(inv_person_ig,
     vertex.label=NA,
     vertex.frame.color=NA,
     vertex.color=V(inv_person_ig),
     vertex.size=2,
     edge.curved=.1,
     main="Inventor's network for top 15 cities",
     sub=("(on edge betweenness of the inventors)"),
     edge.width = edge_betweenness(inv_person_ig))
```

# Top 5 city's innovation scenario over the time

Detaching packages to avoid conflicts between package operations

```{r}
detach(package:igraph)
library(network)
library(ndtv)
```

## Aurich

```{r}
aurich_d_2007 <- (data_main_15_attr %>% 
                    filter(city=="Aurich", app_year==2007) %>% 
                    select(city, appln_id, inv_name)) # for 2007
aurich_d_2016 <- (data_main_15_attr %>%
                    filter(city=="Aurich", app_year==2016) %>%
                    select(inv_name, appln_id)) # for 2016
aurich_2016_2mode <- table(aurich_d_2016)
aurich_2016_adj <- aurich_2016_2mode %*% t(aurich_2016_2mode)
aurich_2016_nw <-  network(aurich_2016_adj)  # convert into 'network' format
```

### Plotting

```{r}
par(mfrow=c(1,2))

render.d3movie(aurich_2016_nw,
               displaylabels = T,
               vertex.cex = 1,
               vertex.colour = rainbow(6),
               edge.col = "darkgrey",
               vertex.border = NA,
               output.mode="htmlWidget")
```
